Disparity tables for the Appendix

### 2017-12-20 analyses/01-extract-data-for-analyses.Rmd
Add author info

---
title: "Extracting data for time slice analyses"
author: "Natalie Cooper and Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 6
    fig_height: 6
---

>>>>

---
title: "Extracting data for time slice analyses"
author: "Thomas Guillerme and Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 6
    fig_height: 6
---

### 2017-12-20 analyses/12-appendix-disparity-tables.Rmd
Add author info

---
title: "Disparity tables for the appendix q"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---

>>>>

---
title: "Disparity tables for the Appendix"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---
